A New Approach for Parallel Functional Arrays

### 2016-03-11 Paper/paper.tex
Add cost dynamics for regular functions

$L$ contains the usual arithmetic types, such as the natural numbers, and numerical operations such as sums and products. Our dynamics are given by the judgement $e \Downarrow v$ which means that expression $e$ evaluates to $v$. Dynamics for function application and fork-join are given as examples.

$$\frac{e_1 \Downarrow v_1 \;\;\; e_2 \Downarrow v_2}{e_1 || e_2 \Downarrow (v_1, v_2)} \text{ (fork-join)}$$
$$\frac{f \Downarrow \lambda x . e \;\;\; y \Downarrow v}{f \; y \Downarrow [v/x]e} \text{ (function-app)}$$

@@

We give the cost dynamics for expressions in the language: (insert cost dynamics for standard functions later)

>>>>

$L$ contains the usual arithmetic types, such as the natural numbers, and numerical operations such as sums and products. Lambda expressions and constants (including arrays) are terminal values in our language. Our dynamics are given by the judgement $e \Downarrow v$ which means that expression $e$ evaluates to $v$. Dynamics for function application and fork-join are given as examples.

$$\frac{e_1 \Downarrow v_1 \;\;\; e_2 \Downarrow v_2}{e_1 || e_2 \Downarrow (v_1, v_2)} \text{ (fork-join)}$$
$$\frac{f \Downarrow \lambda x . e \;\;\; y \Downarrow v \;\;\; [v/x]e \Downarrow v'}{f \; y \Downarrow v'} \text{ (function-app)}$$

@@

We give the cost dynamics for arbitrary expressions in our language:

$$\frac{}{\delta; c \Downarrow \delta; c; 1; 1} \text{ (constants)}$$

$$\frac{\delta; e_1 \Downarrow \delta'; \lambda x . e; w_1 ; s_1 \;\;\; \delta'; e_2 \Downarrow \delta'';v; w_2 ; s_2 \;\;\; \delta''; [v/x]e \Downarrow \delta'''; v'; w_3 ; s_3}{\delta; e_1 \; e_2 \Downarrow \delta'''; v'; 1+w_1+w_2+w_3; 1+s_1+s_2+s_3}$$

$$\frac{\delta; e_1 \Downarrow \delta'; true; w_1; s_1 \;\;\; \delta'; e_2 \Downarrow \delta''; v; w_2; s_2}{\delta; \text{if } e_1 \text{ then } e_2 \text{ else } e_3 \Downarrow \delta''; v; 1+w_1+w_2; 1+s_1+s_2} \text{ (if-true)}$$

$$\frac{\delta; e_1 \Downarrow \delta'; false; w_1; s_1 \;\;\; \delta'; e_3 \Downarrow \delta''; v; w_2; s_2}{\delta; \text{if } e_1 \text{ then } e_2 \text{ else } e_3 \Downarrow \delta''; v; 1+w_1+w_2; 1+s_1+s_2} \text{ (if-false)}$$
